### 2019-09-20 bp_discussion.tex
updated

\subsection{Tai Chi Intervention}
As we described early, the second half of the field study data
collection involved an intervention of Tai Chi. This intervention was
used to keep participants motivated to continue over the long study
period.  To investigate whether the intervention had any effect, we
linked participants tai chi session attendance data with their
self-reported percieved stress levels. Building a linear mixed model
with tai chi attendance as a random effect, we found that tai chi
attendance contributed a small amount to decreased stress in the work
week immediately following the tai chi session (slope of -0.188, p <
0.05). However, we did not find a connection between attendance and
stress on the day of the session suggesting that tai chi might have
long-term effects, but is not conducive at relieving stress close
in time to the intervention.

>>>>

\subsection{Tai Chi Intervention}
As we described early, the second half of the field study data
collection involved an intervention of tai chi. This intervention was
used to keep participants motivated to continue over the long study
period.  To investigate whether the intervention had any effect, we
linked participants tai chi session attendance data with their
self-reported percieved stress levels. Building a linear mixed model, we found that tai chi
attendance contributed a small amount to decreased stress in the work
week immediately following the tai chi session (slope of -0.188, p <
0.05). However, we did not find a connection between attendance and
stress on the day of the session suggesting that tai chi might have
long-term effects, but is not conducive at relieving stress close
in time to the intervention.

### 2019-09-20 bp_results_1.tex
Not sure what changed
updated

@@

%% \subsubsection{Tai Chi Intervention}
%% We linked participants tai chi session attendance data with their self-reported percieved stress levels. Building a linear mixed model with tai chi attendance as a random effect, we found that tai chi attendance contributed a small amount to decreased stress in the work week immediately following the tai chi session (slope of -0.188, p < 0.05). However, we did not find a connection between attendance and stress on the day of the session.

>>>>

\begin{figure}
  \centering
      \includegraphics[width=0.5\textwidth]{dailystress_s1.pdf}
      \includegraphics[width=0.5\textwidth]{dailystress_s3.pdf}
  \caption{The day-to-day stress levels reported by two participants (S1 and S3) are shown. The y-axis represents values on the 5-point Likert scale we asked participants to respond with ranging from 1/Not at all stressed to 5/Extremely stressed. The x-axis represents the day of the study on which the value was recorded (from 0-45). The x-axes are slightly different for the 2 participants as they did not begin and end the study on exactly the same days.}
   \vspace*{-2mm}
\end{figure}

@@
